A Formal Model of Checked C

### 2023-01-15 sandp23/implementation.tex
Minor additions to implementation

\noindent\emph{Handling Calls to Tainted Functions}:
In~\cregion, we also need to modify calls to tainted functions as they execute inside the sandbox (separate address space) and thus cannot be invoked as regular functions.
We rewrite all calls to tainted functions with corresponding sandbox invocations.
For instance, we modify the call to~\code{process_req1} in~\lst{lst:final} as below:
\begin{minted}[mathescape, escapeinside=||, fontsize=\footnotesize]{diff}
case REQ1: 
- rc = process_req1(buff); 
+ rc = .....
\end{minted}
\aravind{Arun, please fix the above example with the exact details.}

@@

\subsubsection{Generating~\ucregion Source Partition}
\label{subsubsec:genucregion}
We create~\ucregion partition by first copying all functions marked as~\code{_Tained} and~\code{_Mirror}.
Next, we convert the partition into regular C by replacing all~\systemname{} tainted types with the corresponding C types.
For instance:~\code{_T_Array_ptr<char>} will be replaced with~\code{char *}.
The~\code{read_msg} function signature in~\lst{} will be modified as shown below:
\begin{minted}[mathescape, escapeinside=||, fontsize=\tiny]{diff}
size_t read_msg(int sock_fd, char *msg,
-                             size_t sz) __Tainted {
+                             size_t sz) {
\end{minted}

>>>>

\noindent\emph{Handling Calls to Tainted Functions}:
In~\cregion, we also need to modify calls to tainted functions as they execute inside the sandbox (separate address space) and thus cannot be invoked as regular functions.
However, modifying every call site of tainted functions is tedious and also requires precise pointer analysis~\cite{milanova2002precise} to handle indirect calls through function pointers.

We handle this by~\emph{indirection}: Instead of modifying the call sites, we modify the body of tainted functions to invoke the corresponding function in the sandbox.
For instance, we modify the body of tainted function~\code{process_req1} (\lst{lst:final}) in~\cregion as below:
\begin{minted}[mathescape, escapeinside=||, fontsize=\footnotesize]{diff}
int process_req1(char *msg, size_t m_l) _Tainted {
- int rc = -1, i;
- if (m_l > MIN_SIZE) {
- ...
+ HOW DO WE HANDLE SANDBOX CALL.
}
\end{minted}
This ensures that all calls (even through function pointers) to the tainted function~\code{process_req1} are redirected to the sandbox.
\aravind{Arun, add the call on how to call sandbox function.}

@@

\subsubsection{Generating~\ucregion Source Partition}
\label{subsubsec:genucregion}
We create~\ucregion partition by first copying all functions marked as~\code{_Tained} and~\code{_Mirror}.
Next, we convert the partition into regular C by replacing all~\systemname{} tainted types with the corresponding C types.
For instance:~\code{_T_Array_ptr<char>} will be replaced with~\code{char *}.
The~\code{read_msg} function signature in~\lst{lst:final} will be modified as shown below:
\begin{minted}[mathescape, escapeinside=||, fontsize=\tiny]{diff}
size_t read_msg(int sock_fd, char *msg,
-                             size_t sz) _Tainted {
+                             size_t sz) {
\end{minted}
